SMASH companion source code repository

### 2018-11-06 analysis/index.Rmd
Greatly simplified the README.

---
title: "SMASH companion code resources"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
---

>>>>

---
title: "SMASH companion source code repository"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
---

This repository contains source code and data accompanying our manuscript:

> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
signals.* [arXiv:1709.10066](http://arxiv.org/abs/1605.07787).

reproduce some of the
empirical results presented in [Xing & Stephens (2016)][smashr-preprint].
The new methods can be found in the [smashr package][smashr].

If you find a bug, please post an [issue][issues].

## Citing this work

If you find any of the source code in this repository useful for your
work, please cite our paper:

> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
signals.* [arXiv:1709.10066](http://arxiv.org/abs/1605.07787).

## License

Copyright (c) 2016-2018, Zhengrong Xing, Peter Carbonetto * Matthew
Stephens.

All source code and software in this repository are made available
under the terms of the
[MIT license](https://opensource.org/licenses/mit-license.html). See
the [LICENSE](LICENSE) file for the full text of the license.

## Credits

This project was developed by [Zhengrong Xing][zhengrong] at the
University of Chicago, with support and contributions from
[Peter Carbonetto][peter] and [Matthew Stephens][matthew].

[smashr]: https://github.com/stephenslab/smashr
[smashr-preprint]: http://arxiv.org/abs/1605.07787
[dscr-smash]: https://github.com/stephenslab/dscr-smash
[issues]: https://github.com/stephenslab/smash-paper/issues
[zhengrong]: https://github.com/zrxing
[peter]: http://pcarbo.github.io
[matthew]: http://stephenslab.uchicago.edu
